### 2020-11-30 Research Report - Boverhof/Tex report/main.tex

@@

\subsubsection{Experimental setup}
The experimental setting for data collection is the spaceship videogame Empty Epsilon, in which the respondent is required to carry out tasks on a virtual spaceship \cite{daid2016empty}. This experiment is instituted by the Brain Computer Interfaces (BCI) testbed lab, hosted by the University of Twente (UT) and carried out in cooperation with Thales. The experiment constituted three different segments, during each of which respondents had to carry out different tasks, all aiming to measure workload. Each segment consists of six small sessions of roughly 5-10 minutes. These sessions varied in difficulty, including two easy, two intermediate and two hard sessions per segment. A schematic overview of the experimental structure is depicted as table \ref{table:expsetup}. After each of the 18 segments, respondents filled in the TLX questionnaire consisting of 6 questions each, resulting in 18 filled in questionnaires. Each questionnaire inquired upon the degree to which the respondent experienced workload during the previous session. These ratings will be used as labels in later training. Within each segment, the order in which the sessions (varying in difficulty) were presented have been randomized. The order in which the segments were administrated were not random. Between every three sessions, respondents were requested to take a short 2 minute break.
\bgroup
\def\arraystretch{1.6}%  
\begin{table}[h]
\centering
\caption{Experimental setup: Number of sessions per segment and difficulty setting}
\label{table:expsetup}
\begin{tabular}{llll}
                               & Easy                   & Intermediate           & Hard                   \\ \cline{2-4} 
\multicolumn{1}{l|}{Segment 1} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
\multicolumn{1}{l|}{Segment 2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
\multicolumn{1}{l|}{Segment 3} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
\end{tabular}
\end{table}
\egroup

\subsubsection{Participants}
In total, \# respondents have participated in the study.

\subsubsection{Data collection and Synchronization}
About streaming to LSL, and the utilized devices.

>>>>

\subsubsection{Experimental setup}
The experimental setting for data collection is the spaceship videogame Empty Epsilon, in which the respondent is required to carry out tasks on a virtual spaceship \cite{daid2016empty}. This experiment is instituted by the Brain Computer Interfaces (BCI) testbed lab, hosted by the University of Twente (UT) and carried out in cooperation with Thales group Hengelo. The experiment constituted three different segments, during each of which respondents had to carry out different tasks, all aiming to measure workload. Each segment consists of six small sessions of roughly 5-10 minutes. These sessions varied in difficulty, including two easy, two intermediate and two hard sessions per segment. A schematic overview of the experimental structure is depicted as table \ref{table:expsetup}. After each of the 18 segments, respondents filled in the TLX questionnaire consisting of 6 questions each, resulting in 18 filled in questionnaires. Each questionnaire inquired upon the degree to which the respondent experienced workload during the previous session. These ratings will be used as labels in later training. Within each segment, the order in which the sessions (varying in difficulty) were presented have been randomized. The order in which the segments were administrated were not random. Between every three sessions, respondents were requested to take a short 2 minute break.
\bgroup
\def\arraystretch{1.6}%  
\begin{table}[h]
\centering
\caption{Experimental setup: Number of sessions per segment and difficulty setting}
\label{table:expsetup}
\begin{tabular}{llll}
                               & Easy                   & Intermediate           & Hard                   \\ \cline{2-4} 
\multicolumn{1}{l|}{Segment 1} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
\multicolumn{1}{l|}{Segment 2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
\multicolumn{1}{l|}{Segment 3} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
\end{tabular}
\end{table}
\egroup

\subsubsection{Participants}
In total, twenty-five respondents are participating in the study. Currently, the data is still in the process of being collected, for which no additional descriptive statistics can be presented in the prevailing section. The respondents are students, recruited from the University of Twente. Recruitment has been conducted with Sona, which is a cloud-based participant management system. Requirements were that respondents didn't have constraints that might interfere with the utilized sensors, such as for example a pacemaker. This is assessed by means of a short demographic questionnaire prior to the experiment. Additionally, the respondents are made aware of ethical consent prior to the experiment, with the objective to ensure completely voluntary participation. Respondents were able to draw back from the experiment at any time.

\subsubsection{Data collection and Synchronization}
Data streams stemming from the different modalities are measured on different frequencies, and consequently need to be properly synchronized. This is accomplished by means of a technique called Lab-Streaming Layer (LSL), to which different data streams are streamed during the experiment. LSL properly synchronizes these data streams, records all data into a single file per participant \cite{kothe2018lab}.

@@
